---
title: "Weight of Fish"
author: "Anicia Friend"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch
```{r}
library(leaps)
regsubsets.out<-regsubsets(Weight ~.,data=Perch,nbest=1,nvmax=NULL,
                           force.in=NULL,force.out=NULL,method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```


```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main ="adjr2")
```



### Best Models

The best model is the two element model; H & W models. 

### Best Two regressor model

The best two regressive model is also the model H & W.

## Pike

```{r}
library(leaps)
regsubsets.out<-regsubsets(Weight ~.,data=Pike,nbest=1,nvmax=NULL,
                           force.in=NULL,force.out=NULL,method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```


```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main ="adjr2")
```



### Best Models

The best model is model5, corresponding to L1-L2-L3-H-W

### Best Two regressor model

The best two regression model is model12; L1-L3

The best model is different to the best two regression models so we will run ANOVA. 

```{r}
model5=lm(Weight~.,data=Pike)
summary.lm(model5)
model2=lm(Weight~ .-Length2-Height-Width, data=Pike)
model3=lm(Weight~ .-Length2-Height-Width, data=Pike)
anova(model5,model2)
```


## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements